Cleaning Script

### 2025-02-21 code/processing-code/processingfile-v1.qmd
Woops forgot to close Rstudio

# Additionally, add a column about new cases for further analysis down the line.
merged_df_clean <- merged_df_clean %>%
  arrange(state, county, date) %>%  # Sort (Need to make sure calculations occur between the correct states/counties and in order)
  group_by(state, county) %>%  # Group by state and county to calculate new cases within each county
  mutate(new_cases = c(NA, diff(total_cases))) %>%  # Calculate new cases
  ungroup()  # Ungroup after the calculation
```

>>>>

# Additionally, add a column about new cases for further analysis down the line.
merged_df_clean <- merged_df_clean %>%
  arrange(state, county, date) %>%  # Sort (Need to make sure calculations occur between the correct states/counties and in order)
  group_by(state, county) %>%  # Group by state and county to calculate new cases within each county
  mutate(new_cases = c(NA, diff(total_cases))) %>%  # Calculate new cases
  ungroup()  # Ungroup after the calculation

# Create column for mean average mobiltiy change for that given day and location. I omitted mobility changes to residencies because that may be more of an indication of who is at home.
merged_df_clean <- merged_df_clean %>%
  arrange(state, county, date) %>%  # Sort to ensure correct calculations
  group_by(state, county) %>%  # Group by state and county
  mutate(average_mobility = rowMeans(
    cbind(transit_stations_percent_change_from_baseline, 
          parks_percent_change_from_baseline, 
          retail_and_recreation_percent_change_from_baseline, 
          grocery_and_pharmacy_percent_change_from_baseline, 
          workplaces_percent_change_from_baseline), 
    na.rm = TRUE)) %>%
  ungroup()
